Blockchain Consensus Protocol with\\Horizontal Scalability

### 2017-07-27 presentation/presentation.tex
Use TUD template for presentation

% Copyright 2004 by Till Tantau <tantau@users.sourceforge.net>.
%
% In principle, this file can be redistributed and/or modified under
% the terms of the GNU Public License, version 2.
%
% However, this file is supposed to be a template to be modified
% for your own needs. For this reason, if you use this file as a
% template and not specifically distribute it as part of a another
% package/program, I grant the extra permission to freely copy and
% modify this file as you see fit and even to delete this copyright
% notice.

\documentclass{beamer}

% There are many different themes available for Beamer. A comprehensive
% list with examples is given here:
% http://deic.uab.es/~iblanes/beamer_gallery/index_by_theme.html
% You can uncomment the themes below if you would like to use a different
% one:
%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
%\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{boxes}
%\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
\usetheme{default}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
%\usetheme{Madrid}
%\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}

\usepackage{amsfonts}
\usepackage{graphicx}
\graphicspath{{../figures/}}
\usepackage[noend]{algpseudocode}
\usepackage{algorithm}

@@

\setbeameroption{show notes}

\title{Blockchain Consensus Protocol with Horizontal Scalability}

% A subtitle is optional and this may be deleted
% \subtitle{Optional Subtitle}

@@

% \date{Conference Name, 2013}
\date{\today}
% - Either use conference name or its abbreviation.
% - Not really informative to the audience, more for people (including
%   yourself) who are reading the slides online

\titlegraphic{\includegraphics[width=4cm]{logo}}

@@

\begin{frame}{Research question}
    How do we design a \emph{blockchain consensus protocol} that is \emph{fault tolerant},
    \emph{scalable} and can reach \emph{global consensus?}
    \note{
      \begin{itemize}
      \item Blockchain consensus protocol---independent of the application, like PoW (not PoS)
      \item Byzantine fault tolerance---if some number of nodes are malicious then the system should continue to function
      \item Horizontal scalability---if every node make transactions at the same rate, then the global throughput should increase
      \item Global consensus---all node should agree on a global state, useful for some applications, e.g. digital cash
      \end{itemize}
    }
\end{frame}

\begin{frame}{Inspiration}
  \begin{itemize}
    \item A restaurant owner does not report all of its transactions with an central authority
    \item Ocassionally a customer may leave without paying and this event is reported to a central authority
    \item Our blockchain system achieves scalability using a similar idea
  \end{itemize}
\end{frame}

@@

\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{trustchain-good-cp}
  \centering
  \caption{TX block is a six-tuple: $t_{u, i} = \langle \textsf{H}(b_{u, i - 1}), i, txid, pk_v, m, sig_u \rangle$.
    CP block is a five-tuple: $c_{u, i} = \langle \textsf{H}(b_{u, i-1}), i, \textsf{H}(\C_r), r, sig_u \rangle$.}
  \end{figure}
  \note{
    \begin{itemize}
      \item In this example there are three nodes
      \item Squares are TX blocks and circles are CP blocks
      \item Explain the block content in caption
      \item The dotted line represent pairs of TX blocks
      \item Geared with the understanding of our data structure, we are ready to talk about the consensus protocol
    \end{itemize}
  }
\end{frame}

@@

\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{trustchain-1}
  \centering
  \caption{Suppose we are in a state where $\C_{r - 1}$ has just been agreed by some facilitators but not yet propagated.}
  \end{figure}
\end{frame}

\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{trustchain-2}
  \centering
  \caption{Nodes receive consensus result $\C_{r - 1}$,
    first $n$ nodes ordered by $\textsf{H}(\C_r || pk)$ become $\F_{r-1}$,
    send the new CP blocks to $\F_{r-1}$.}
  \end{figure}
\end{frame}

\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{trustchain-3}
  \centering
  \caption{Transactions carry on as usual in round $r$,
  while facilitators are trying to reach consensus on the new CP blocks concurrently.}
  \end{figure}
\end{frame}

\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{trustchain-4}
  \centering
  \caption{$\F_{r-1}$ agree and disseminate $\C_r$,
  CP blocks at round $r-1$ ($c_{a, 6}, c_{b, 4}, c_{c,8}$) should be in $\C_r$.}
  \end{figure}
\end{frame}

@@

\begin{frame}{\subsecname:~properties}
\begin{itemize}
    \item \emph{Agreement}:
        If any correct node decides on the validity (except when it is \emph{unknown}) of a transaction,
        then all other correct nodes are able to reach the same conclusion or \emph{unknown}.
    \item \emph{Correctness}:
        The validation protocol outputs the correct result
        according to the aforementioned validity definition.
    \item \emph{Liveness}:
        Any valid (invalid) transaction is marked as validated (invalid) eventually.
\end{itemize}
\note{Liveness is not possible in our case because malicious nodes can simply go offline or refuse to respond,
but the other two properties are possible.}
\end{frame}

@@

\subsection{Correctness of the consensus protocol}
\begin{frame}{\subsecname}
\begin{theorem}
For all rounds,
the consensus protocol satisfies agreement, validity, fairness and termination.
\end{theorem}
\begin{proof}(sketch)
Because consensus result are eventually delivered and the properties of Byzantine consensus,
we get agreement, validity and termination.
Fairness is from the fact that we model $\textsf{H}(\cdot)$ as a random oracle (RO) and the input to the RO is different for every node,
thus the list of nodes ordered by $\textsf{H}(\C_r || pk )$ is a random permutation of those nodes.
\end{proof}
\end{frame}

\subsection{Correctness of the validation protocol}
\begin{frame}{\subsecname}
\begin{theorem}
If any correct node decides on the validity (except when it is \emph{unknown}) of a transaction according to the validity definition,
then all other correct nodes are able to reach the same conclusion or \emph{unknown}.
\end{theorem}
\begin{proof}(sketch)
Proof by contradiction.
For this attack to work, the adversary must be able to create two different fragments but with the same checkpoint enclosure.
We model $\textsf{H}(\cdot)$ as a RO, so the adversary need to query the RO a exponential\footnote{In terms of the security parameter.} number of times.
But the adversary can only query the RO a polynomial number of times.
\end{proof}
\end{frame}

@@

\begin{frame}{Throughput vs population size (random neighbour)}
  \begin{figure}[h]
  \includegraphics[width=1.0\textwidth]{neighbour-random/throughput-vs-population}
  \centering
  \end{figure}
\end{frame}

\begin{frame}{Throughput vs population size (fixed neighbour)}
  \begin{figure}[h]
  \includegraphics[width=1.0\textwidth]{neighbour-fixed/throughput-vs-population}
  \centering
  \end{figure}
\note{No need to request for fragment every time a TX needs to be validated. Upon receiving a fragment, validate as many TX as possible.}
\end{frame}

\section{Conclusion}
\begin{frame}{\secname}
    How do we design a \emph{blockchain consensus protocol} that is \emph{fault tolerant},
    \emph{scalable} and can reach \emph{global consensus?}
\begin{itemize}
  \item[\checkmark] Fault tolerant up to $t$ nodes
  \item[\checkmark] Horizontal scalability
  \item[\checkmark] Global consensus
\end{itemize}
\end{frame}

>>>>

% TU Delft beamer template
% Author: Erwin Walraven (initial version was created by Maarten Abbink)
% Delft Universiy of Technology

\documentclass{beamer}
\usepackage[english]{babel}
\usepackage{calc}
\usepackage[absolute,overlay]{textpos}
\usepackage{graphicx}
\graphicspath{{../figures/}}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{comment}
\usepackage{MnSymbol,wasysym}
\usepackage[noend]{algpseudocode}
\usepackage{algorithm}

\setbeamertemplate{navigation symbols}{} % remove navigation symbols
\mode<presentation>{\usetheme{tud}}

@@

% \setbeameroption{show notes}

\title{Blockchain Consensus Protocol with\\Horizontal Scalability}
% \subtitle{Optional Subtitle}

@@

% \date{Conference Name, 2013}
\date{\today}

@@

\begin{frame}{Research question}
  \begin{block}{}
    How do we design a \emph{blockchain consensus protocol} that is \emph{fault tolerant},
    \emph{scalable} and can reach \emph{global consensus?}
  \end{block}
    \note{
      \begin{itemize}
      \item Blockchain consensus protocol---independent of the application, like PoW (not PoS)
      \item Byzantine fault tolerance---if some number of nodes are malicious then the system should continue to function
      \item Horizontal scalability---if every node make transactions at the same rate, then the global throughput should increase
      \item Global consensus---all node should agree on a global state, useful for some applications, e.g. digital cash
      \end{itemize}
    }
\end{frame}

\begin{frame}{Inspiration}
  \begin{itemize}
    \item A restaurant owner does not report all of its transactions with an central authority
    \item Occasionally a customer may leave without paying and this event is reported to a central authority
    \item Our blockchain system achieves scalability using a similar idea
  \end{itemize}
\end{frame}

@@

\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.67\textwidth]{trustchain-good-cp}
  \centering
  \caption{TX block is a six-tuple: $t_{u, i} = \langle \textsf{H}(b_{u, i - 1}), i, txid, pk_v, m, sig_u \rangle$.
    CP block is a five-tuple: $c_{u, i} = \langle \textsf{H}(b_{u, i-1}), i, \textsf{H}(\C_r), r, sig_u \rangle$.}
  \end{figure}
  \note{
    \begin{itemize}
      \item In this example there are three nodes
      \item Squares are TX blocks and circles are CP blocks
      \item Explain the block content in caption
      \item The dotted line represent pairs of TX blocks
      \item Geared with the understanding of our data structure, we are ready to talk about the consensus protocol
    \end{itemize}
  }
\end{frame}

@@

\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.67\textwidth]{trustchain-1}
  \centering
  \caption{Suppose we are in a state where $\C_{r - 1}$ has just been agreed by some facilitators but not yet propagated.}
  \end{figure}
\end{frame}

\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.67\textwidth]{trustchain-2}
  \centering
  \caption{Nodes receive consensus result $\C_{r - 1}$,
    first $n$ nodes ordered by $\textsf{H}(\C_{r-1} || pk)$ become $\F_{r-1}$,
    send the new CP blocks to $\F_{r-1}$.}
  \end{figure}
\end{frame}

\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.67\textwidth]{trustchain-3}
  \centering
  \caption{Transactions carry on as usual in round $r$,
  while facilitators are trying to reach consensus on the new CP blocks concurrently.}
  \end{figure}
\end{frame}

\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.67\textwidth]{trustchain-4}
  \centering
  \caption{$\F_{r-1}$ agree and disseminate $\C_r$,
  CP blocks at round $r-1$ ($c_{a, 6}, c_{b, 4}, c_{c,8}$) should be in $\C_r$.}
  \end{figure}
\end{frame}

@@

\begin{frame}{\subsecname:~properties}
\begin{itemize}
    \item \emph{Agreement}:
        If any correct node decides on the validity of a transaction (except when it is \emph{unknown}),
        then all other correct nodes are able to reach the same conclusion or \emph{unknown}.
    \item \emph{Correctness}:
        The validation protocol outputs the correct result
        according to the aforementioned validity definition.
    \item \emph{Liveness}:
        Any valid (invalid) transaction is marked as validated (invalid) eventually.
\end{itemize}
\note{Liveness is not possible in our case because malicious nodes can simply go offline or refuse to respond,
but the other two properties are possible.}
\end{frame}

@@

\subsection{Correctness of the consensus protocol}
\begin{frame}{\subsecname}
\begin{theorem}
For all rounds,
the consensus protocol satisfies agreement, validity, fairness and termination properties.
\end{theorem}
\begin{proof}(sketch)
Because consensus result are eventually delivered and the properties of Byzantine consensus,
we get agreement, validity and termination.
Fairness is from the fact that we model $\textsf{H}(\cdot)$ as a random oracle (RO) and the input to the RO is different for every node,
thus the list of nodes ordered by $\textsf{H}(\C_r || pk )$ is a random permutation of those nodes.
\end{proof}
\end{frame}

\subsection{Correctness of the validation protocol}
\begin{frame}{\subsecname}
\begin{theorem}
  The validation protocol satisfies agreement and correctness properties.
\end{theorem}
\begin{proof}(sketch)
Proof by contradiction.
For this attack to work, the adversary must be able to create two different fragments but with the same checkpoint enclosure.
We model $\textsf{H}(\cdot)$ as a RO, so the adversary need to query the RO a exponential\footnote{In terms of the security parameter.} number of times.
But the adversary can only query the RO a polynomial number of times.
Hence we have agreement.
Correctness follows directly the use of the $\textsf{get\_validity}(\cdot)$ function.
\end{proof}
\end{frame}

@@

\begin{frame}{Throughput vs population size (random neighbour)}
  \begin{figure}[h]
  \includegraphics[width=0.9\textwidth]{neighbour-random/throughput-vs-population}
  \centering
  \end{figure}
\end{frame}

\begin{frame}{Throughput vs population size (fixed neighbour)}
  \begin{figure}[h]
  \includegraphics[width=0.9\textwidth]{neighbour-fixed/throughput-vs-population}
  \centering
  \end{figure}
\note{No need to request for fragment every time a TX needs to be validated. Upon receiving a fragment, validate as many TX as possible.}
\end{frame}

\section{Conclusion}
\begin{frame}{\secname}
  \begin{block}{Research question}
    How do we design a \emph{blockchain consensus protocol} that is \emph{fault tolerant},
    \emph{scalable} and can reach \emph{global consensus?}
  \end{block}
Our system achieve the following
\begin{itemize}
  \item Fault tolerant up to $t$ nodes
  \item Horizontal scalability
  \item Global consensus on CP blocks
\end{itemize}
\end{frame}
